### 2015-07-07 chapters/ipa_meets_unicode.tex
initial notes for IPA extensions

>>>>

\begin{comment}
\subsection{IPA (practical) extensions}

The IPA extensions cover speech sounds beyond the sound systems of the world's languages, including symbols for pathological speech and paralinguistic functions (e.g.\ Braille?).

- pathological speech
- paralinguistic functions (Braille?)

As noted in Section \ref{}, extensions to the IPA -- in particular ``large-scale'' extensions --

% Englebretson2009.pdf
http://www.ruf.rice.edu/~reng/englebretson2009.pdf

X-SAMPA was an ASCII transliteration and is still purposeful for several programs

There is also the extensions of the IPA designed for disordered speech, although the symbols are occasionally used for transcribing phonetic detail in ``normal'' speech or also cross-linguistic rarities.\footnote{\url{http://phoible.github.io/conventions/}}

% Unicode has its own history; for a summary: \url{http://www.unicode.org/history/summary.html}

https://www.phon.ucl.ac.uk/home/wells/ipa-unicode.htm

Computer codes for phonetic symbols
EslingGaylord1993

\end{comment}
